Scaling up the hyperparameter grid for Naomi

### 2023-06-12 src/dev_scale-grid/scale-grid.Rmd
Temporarily keep version of tmb.rds from last archived orderly repo that ran without this bug #50 #49

```{r, class.source = 'fold-hide'}
compile("naomi_simple.cpp")
dyn.load(dynlib("naomi_simple"))

tmb <- readRDS("depends/tmb.rds")
fit <- tmb$fit
```

@@

```{r}
sd_out <- sdreport(obj = fit$obj, par.fixed = fit$par, getJointPrecision = TRUE)
```

>>>>

```{r, class.source = 'fold-hide'}
TMB::compile("naomi_simple.cpp")
dyn.load(TMB::dynlib("naomi_simple"))

# tmb <- readRDS("depends/tmb.rds")
tmb <- readRDS("tmb.rds")
fit <- tmb$fit
```

@@

```{r}
testrun <- parallel::mcparallel({TMB::sdreport(obj = fit$obj, par.fixed = fit$par, getJointPrecision = TRUE)})
sd_out <- parallel::mccollect(testrun, wait = TRUE, timeout = 0, intermediate = FALSE)
```
